\documentclass[12pt, titlepage]{article}

\usepackage{graphicx} % Allows for images
\usepackage{wrapfig} % Allows for text wrapping around images
\usepackage{hyperref} % Allows for hyperlinks
\usepackage{siunitx} % Allows for SI units
\usepackage{amsmath} % Allows for math
\usepackage{enumerate} % Allows for custom enumerations
\usepackage{xcolor} % Allows for custom colors
\usepackage{tikz, tcolorbox} % Allows for custom boxes
\usepackage{microtype} % Allows for better text alignment
\usepackage{listings} % Allows for code listings
\usepackage{booktabs} % Allows for better tables
\usepackage{float} % Allows for better figure placement
\usepackage{geometry} % Allows for custom page geometry
\usepackage{fancyhdr} % Allows for custom headers and footers
\usepackage{caption} % Allows for custom captions
\usepackage{array} % Required package for specifying column width and line in the table
\usepackage{changepage} % Required for the adjustwidth environment to temporarily widen margins

\fancypagestyle{myarticlestyle}{
    \fancyhf{} % Clear header and footer
    \fancyhead[L]{\leftmark} % Section name on the left
    \fancyhead[R]{\thepage} % Page number on the right
}
\fancypagestyle{tocstyle}{
    \fancyhf{} % Clear header and footer
    \fancyhead[L]{CONTENTS} % Section name on the left
    \fancyhead[R]{\thepage} % Page number on the right
}

\pagestyle{myarticlestyle}
\setlength{\headheight}{15pt}

\begin{document}
\tableofcontents
\listoffigures
\listoftables
\thispagestyle{tocstyle}
\newpage
\section{Objectives}
\begin{enumerate}
    \item \textbf{Determination of Buckling Loads:}
    \begin{itemize}
        \item Investigate and quantify the buckling loads of slender pin-ended bars through experimental procedures.
        \item Analyze the relationship between applied loads and the resulting center deflections for each tested bar.
    \end{itemize}

    \item \textbf{Comparison of Theoretical and Experimental Critical Loads:}
    \begin{itemize}
        \item Assess and calculate the theoretical critical loads for the pin-ended bars using relevant analytical models.
        \item Perform experimental tests to determine the critical loads for each bar.
        \item Conduct a comprehensive comparison between the theoretical predictions and the experimentally obtained critical loads for all tested bars.
    \end{itemize}
\end{enumerate}

Through these objectives, the aim is to enhance our understanding of the
buckling behavior of slender pin-ended bars and to evaluate the accuracy of
theoretical predictions in relation to practical experimental outcomes.
\newpage
\section{Procedure}
\begin{enumerate}
    \item \textbf{Bar Insertion and Setup:}
    \begin{itemize}
        \item Insert one of the bars between the supports, ensuring that the ball bearing at the ends seats firmly.
        \item Orient the larger dimension of the cross-section parallel to the floor.
        \item Position the displacement transducer to measure the vertical deflection of the bar.
    \end{itemize}

    \item \textbf{Moment of Inertia Calculation and Critical Load Prediction:}
    \begin{itemize}
        \item Calculate the minimum moment of inertia for the inserted bar.
        \item Predict the critical load for the bar based on the calculated moment of inertia.
    \end{itemize}

    \item \textbf{Data Collection Using Dalite Datascan Configurator:}
    \begin{itemize}
        \item Open the Dalite Datascan Configurator at the DB2Bc.OVL file.
        \item Click on the "monitor every second" window.
        \item Verify that the initial reading for the electrical potentiometer is zero.
        \item Apply the load increments slowly.
        \item At each increment, record the central deflection.
        \item Continue to increase the load until the column buckles or the central deflection becomes large.
    \end{itemize}

    \item \textbf{Repeat for All Bars:}
    \begin{itemize}
        \item Repeat steps 2 to 4 for all four bars in the experimental setup.
    \end{itemize}
\end{enumerate}

This procedure outlines the steps to insert the bars, calculate relevant
parameters, and conduct the experimental testing using the Dalite Datascan
Configurator. It ensures systematic data collection for each bar in the study.
\newpage
\section{Results}
\newpage
\section{Discussion}
\newpage
\section{Conclusions}
\end{document}
